--- 
title: "Bioinformatics in practice: web development,  program optimization and integration"
author: "Shaoqian Ma"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [packages.bib, ref.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Preface

This is my _first_ book written in **Markdown**. You can download the [github version](https://github.com/MSQ-123/bioinfo_book) locally and render it on your PC. This short book (actually, study notes) introduces some of my bioinformatics practice in cooperation with members of professional IT team. 

## Purpose for writing

I am a big fan of R and computational biology. Research in computational biology should involve innovations that could tweak classic theory and transform it into real-life application (medical treatment, clinical trial, drug discovery, etc.). As global challenge right now is fighting against COVID-19, our team aimed to provide an integrative resource, not only focusing on SARS-CoV-2, but also applicable in future research regarding other viruses. Overall, I think a data schemas is instructive. I hope this notebook would develop into a resource that will grow and change over time as a living book (tracking my knowledge footprints).

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


The **bookdown** package can be installed from CRAN or Github, I recommend downloading the [lastest released](https://github.com/rstudio/bookdown/releases/tag/v0.22) instead of CRAN repos, since the CRAN version can sometimes make you frustrated (Do not ask how I know). 

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

## About me

I’m a big fan of R and data science, also interested in python, java (I plan to systematically learn it), front-end js and back-end SQL (I enjoy using dplyr in R, somehow like using SQL interface). I have developed two R packages either seriously( [CovidMutations](https://cran.r-project.org/web/packages/CovidMutations/index.html) ) or for fun( [chromseq](http://ydl.oregonstate.edu/pub/cran/web/packages/chromseq/index.html) ).  I have writen some articles on [jianshu](https://www.jianshu.com/u/d21e99e5c882) platform last year (2020, when I was a junior student in Xiamen University),  talking about some of my experiences in bioinformatics. For biological scope, I have a broad interest in developmental epigenomics, machine learning in biomedicine, and novel NGS methods (my undergraduate thesis titled: *RNA-seq library construction using low cellular input and 
evaluation of single-cell data analysis pipeline*). 
